Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-11-25 analysis/paper/paper.Rmd
data import

```{r setup, include=FALSE}
suppressMessages(library(tidyverse))
library(glue)
library(ggrepel)

# data from PhD data sheet, not KAS sheet.
mydata <- read.csv("~/koreapaleolithicmobilityoccupation/General_info.csv")

# raw material data from KAS data sheet.
kasr <- read.csv("~/koreapaleolithicmobilityoccupation/Rawmaterial_info.csv")

# assemblage composition data from KAS data sheet.
kasa <- read.csv("~/koreapaleolithicmobilityoccupation/Assemblage_info.csv")

#volume of the cultural layer from KAS data sheet.
kasv <- read.csv("~/koreapaleolithicmobilityoccupation/Dating_info.csv")

dates <- read.csv("~/koreapaleolithicmobilityoccupation/Radiocarbon dates.csv")

>>>>

```{r setup, include=FALSE}
suppressMessages(library(tidyverse))
library(glue)
library(ggrepel)
library(here)

# data from PhD data sheet, not KAS sheet.
mydata <- read.csv(here("analysis/data/raw_data/General_info.csv"))

# raw material data from KAS data sheet.
kasr <- read.csv(here("analysis/data/raw_data/Rawmaterial_info.csv"))

# assemblage composition data from KAS data sheet.
kasa <- read.csv(here("analysis/data/raw_data/Assemblage_info.csv"))

#volume of the cultural layer from KAS data sheet.
kasv <- read.csv(here("analysis/data/raw_data/Dating_info.csv"))

dates <- read.csv(here("analysis/data/raw_data/Radiocarbon dates.csv"))
